---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# tenpuzzle
[![Travis-CI Build Status](https://travis-ci.org/kota7/tenpuzzle.svg?branch=master)](https://travis-ci.org/kota7/tenpuzzle)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/kota7/tenpuzzle?branch=master&svg=true)](https://ci.appveyor.com/project/kota7/tenpuzzle)
[![Ask DeepWiki](https://deepwiki.com/badge.svg)](https://deepwiki.com/kota7/tenpuzzle)

`tenpuzzle` provides a solver for ten puzzle quiz, a game that makes 10 from given numbers by arithmetic calculation.
Target numbers other than 10 are supported.

## Installation

You can install `tenpuzzle` from github with:


```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("kota7/tenpuzzle")
```

## Example

The function `tenpuzzle` solves the quiz.
The return value is string expression that makes the target number.
An empty vector is returned if no such expression exists.

```{r example}
library(tenpuzzle)
tenpuzzle(c(1, 1, 9, 9), 10)
```

The function `countdown` solves the "Number Quiz" from the TV show "Countdown".
The return value is a pair of formulas and values that makes the closest number to the target.

```{r countdown}
countdown(c(75, 50, 2, 3, 8, 7), 812)
```

## Shiny app

Launch locally by:

```{r shiny, eval = FALSE}
tenpuzzle_app()
```

Or visit [shinyapps.io](https://kota.shinyapps.io/tenpuzzle/).
 
## Note on the Complexity

The solver algorithm is not very efficient.  
It may not finish in reasonable time for input of length seven or longer.
